---
title: "Lab 06: Grading the professor part II"
author: "YOUR NAME HERE"
date: "`r Sys.Date()`"
format: 
  html:
    self-contained: true
    toc: true
    toc_float: true
    number_section: false
    highlight: "tango"
    theme: "cosmo"
editor: visual
editor_options: 
  chunk_output_type: console
---

# Reflection prompts

*Respond to each of the following after you have completed all exercises in this assignment*

*(RP1): What were the main concepts covered in this assignment?*

> YOUR ANSWER HERE

*(RP2): What's one thing you understand better after completing these exercises?*

> YOUR ANSWER HERE

*(RP3): What exercise(s) gave you the most trouble? What was difficult about them/where did you get stuck?*

> YOUR ANSWER HERE

```{r}
#| label: load-packages
#| message: false
library(tidyverse) 
library(openintro)
```

# Exercise 1

```{r ex-1}

```

# Exericse 2

```{r ex-2}

```

# Exercise 3

> SLOPE:

> INTERCEPT:

# Exercise 4

> YOUR ANSWER HERE

# Exercise 5

Male professors:

$$equationhere$$ Female professors:

$$equationhere$$

# Exercise 6

> YOUR ANSWER HERE

# Exercise 7

> YOUR ANSWER HERE

# Exercise 8

> YOUR ANSWER HERE

# Exercise 9

```{r ex-9}

```

$$equationhere$$

> YOUR ANSWER HERE

# Exercise 10

```{r ex-10}

```

Male professors:

$$equationhere$$

Female professors:

$$equationhere$$

> YOUR ANSWER HERE
